Davos: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2023-09-17 paper/main.tex
add reference for MIND 2023

Since its initial release, Davos has found use in a variety of applications. In
addition to managing computing environments for multiple prior and ongoing
research studies~\citep{MannEtal23a, OwenMann23, ZimaEtal23}, Davos is being
used by both students and instructors in programming and methods courses such
as Storytelling with Data~\cite{Mann21a} (an open course on data science,
visualization, and communication) and Laboratory in Psychological
Science~\cite{Mann22} (an open course on experimental and statistical methods
for psychology research) to simplify distributing lessons and submitting
assignments, as well as in online demos such as
\texttt{abstract2paper}~\cite{Mann21b} (an example application of
GPT-Neo~\cite{GaoEtal20, BlacEtal21}) to share ready-to-run code that installs
dependencies automatically. The 2023 offering of Neuromatch
Academy~\cite{vanVEtal21} also included an ``experimental'' module that uses
Davos to manage dependencies related to a large language model-based
tutor~\cite{MannEtal23b}.

>>>>

Since its initial release, Davos has found use in a variety of applications. In
addition to managing computing environments for multiple prior and ongoing
research studies~\citep{MannEtal23a, OwenMann23, ZimaEtal23}, Davos is being
used by both students and instructors in programming and methods courses such
as Storytelling with Data~\cite{Mann21a} (an open course on data science,
visualization, and communication), Laboratory in Psychological
Science~\cite{Mann22} (an open course on experimental and statistical methods
for psychology research), and the Methods in Neuroscience at Dartmouth (MIND)
Computational Summer School~\cite{MIND23} (a week-long intensive course on 
computational neuroscience methods) to simplify distributing lessons 
and submitting assignments, as well as in online demos such as
\texttt{abstract2paper}~\cite{Mann21b} (an example application of
GPT-Neo~\cite{GaoEtal20, BlacEtal21}) to share ready-to-run code that installs
dependencies automatically. The 2023 offering of Neuromatch
Academy~\cite{vanVEtal21} also included an ``experimental'' module that uses
Davos to manage dependencies related to a large language model-based
tutor~\cite{MannEtal23b}.
